True versus apparent shapes of astrophysical bow shocks

### 2016-06-07 papers/Paper1/sec-generic-model.tex
Minor corrections to article
Week's changes in figures 2, 7 and respective sections
Add new figures for section 2
Final version (?) of Fig 1

\begin{figure}
\includegraphics[width=\linewidth]{2winds-scheme}
\caption{Schematic representation of the two winds problem. Any point in the shell is located with the coordinates
$(R,\theta)$, and $\theta_1$ is measured from the external wind position}
\label{fig:2-winds}
\end{figure}

@@

In order to contrast different bowshock models, we  derive a set of measurable radii. Each model used should predict them and these predictions can be
compared with observations.

\begin{itemize}
\item Radius at axis of symemtry. Denoted as $R_0$. 
\item Radius of Curvature at the axis of symmetry. Denoted as $R_c$
\item Radius at the  perpendicular direction to the symmetry axis. Denoted as $R_{90}$
\item For open bow shocks, the assymptotic angle. Denoted as $\theta_\infty$
\end{itemize}

\begin{figure}
\includegraphics[width=\linewidth]{ch-radii_ed}
\caption{Schematic representation of the characteristic radii $R_0$, $R_{90}$ and the radius of curvature at the symmetry axis $R_c$}
\end{figure}

>>>>

\begin{figure}
% \includegraphics[width=\linewidth]{2winds-scheme}
\includegraphics[width=\linewidth]{figs/generic-bowshock}
\caption{Quasi-stationary bow shock structure formed by the
  interaction of two supersonic winds.  Lower-left inset box shows the
  case where the inner wind is anisotropic.   
  % the two winds problem. Any point in the shell is located with the
  % coordinates $(R,\theta)$, and $\theta_1$ is measured from the
  % external wind position
}
\label{fig:2-winds}
\end{figure}

The general case of a two-wind interaction bow shock is illustrated in
Figure~\ref{fig:2-winds}.  If the winds are isotropic, then the bow
shock pattern wraps around the weaker of the two sources, in

@@

In order to contrast different bow shock models, we  derive a set of measurable radii. Each model used should predict them and these predictions can be
compared with observations.

\begin{itemize}
\item Radius at axis of symmetry. Denoted as $R_0$. 
\item Radius of Curvature at the axis of symmetry. Denoted as $R_c$
\item Radius at the  perpendicular direction to the symmetry axis. Denoted as $R_{90}$
\item For open bow shocks, the asymptotic angle. Denoted as $\theta_\infty$
\end{itemize}

\begin{figure}
\includegraphics[width=\linewidth]{ch-radii_ed2}
\caption{Schematic representation of the characteristic radii $R_0$, $R_{90}$ and the radius of curvature at the symmetry axis $R_c$}
\end{figure}
